---
title: "Homework #6"
author: "Diana Ballesteros Gonzalez"
date: "11/27/2018"
output: github_document
---

```{r setup}
## Loading the packages
library(tidyverse)
library(purrr)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = 1.0,
  out.width = "90%"
)

set.seed(1)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

### **Problem 1**
```{r}
## Import data & made it tidy 
homicide_data = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = paste(city, state, sep = ", "), 
         resolved = as.numeric(disposition == "Closed by arrest"), 
         victim_age = as.numeric(victim_age),
         victim_race = ifelse(victim_race == "White", "White", "Non-White"), 
         victim_race = fct_relevel(victim_race, "White")) %>% 
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" & 
         city_state != "Kansas City, MO" & city_state != "Tulsa, AL") %>% 
  select(city_state, resolved, victim_age, victim_race, victim_sex)
```

Logistic Regression for Baltimore, MD
```{r}
## Used the glm function to fit a logisitic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. 
fit_logistic = 
  homicide_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, 
      data = ., 
      family = binomial())

## Estimate and confidence intervals of thee adjusted ORs
fit_logistic %>% 
  broom::tidy() %>% 
  filter(term == "victim_raceNon-White") %>% 
  mutate(OR = exp(estimate), 
         lower_limit = exp(estimate - 1.96*std.error), 
         upper_limit = exp(estimate + 1.96*std.error)) %>%
  select(OR, lower_limit, upper_limit) %>% 
  knitr::kable(digits = 3)
```

Estimated ORs for Each City 
```{r}
## Nest and unnest to create a data frame 
nest_glm_res =
  homicide_data %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(resolved ~  victim_race + victim_age + victim_sex,
                                 data = .x, family = binomial)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
  mutate(OR = exp(estimate), 
         lower_limit = exp(estimate - 1.96 * std_error), 
         upper_limit = exp(estimate + 1.96 * std_error)) %>% 
  filter(term == "victim_raceNon-White") %>% 
  select(city_state, term, OR, lower_limit, upper_limit)

## Dataframe with ORs and CI
nest_glm_res %>% 
  knitr::kable(digits = 3)

## Plot showing the estimated ORs and CIs for each city 
nest_glm_res %>% 
  arrange(desc(OR)) %>% 
  mutate(city_state = fct_inorder(city_state)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymax = upper_limit, ymin = lower_limit)) +
  labs(
    x = "Location (City & State)", 
    y = "Estimated Odds Ratio", 
    title = "Estimated Odds Ratio of Resolved Homicide Cases for Non-Whites Compared to Whites throughout the United Sates"
  ) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```

Plot Commentary: 

* The plot shows the decreasing odds ratios for the resolved homicide cases for Non-White folks compared to White folks sorted by city and state. 
* Tampa, FL has the highest OR
* Durham, NC has the widest confidence interval 
* Boston, MA has the smallest OR

### **Problem 2**
```{r}
## Import the data
birthweight = 
  read_csv(file = "./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~ "male",
      babysex == 2 ~ "female"), 
    babysex = fct_relevel(babysex, "male"), 
    
    frace = case_when(
      frace == 1 ~ "White", 
      frace == 2 ~ "Black", 
      frace == 3 ~ "Asian", 
      frace == 4 ~ "Puerto Rican", 
      frace == 8 ~ "Other", 
      frace == 9 ~ "Unknown"),
    frace = fct_relevel(frace, "White"), 
    
    malform = case_when(
      malform == 0 ~ "absent",
      malform == 1 ~ "present"), 
    malform = fct_relevel(malform, "absent"), 
    
    mrace = case_when(
      mrace == 1 ~ "White", 
      mrace == 2 ~ "Black", 
      mrace == 3 ~ "Asian", 
      mrace == 4 ~ "Puerto Rican", 
      mrace == 8 ~ "Other", 
      mrace == 9 ~ "Unknown"), 
    mrace = fct_relevel(mrace, "White")
    )
```

### **Model 1** 

Description of the modeling process: 

* I used mother's race, mother's age, and the the length of the baby are some factors that could potentially affect the baby's birthweight. I included race because some research shows that race can play a role in the baby's birthweight, in addition to morther's age and length of the baby. Since "bwt" is continuous, I used "lm" as the basis for the model. 

```{r}
## Model 1 
model_1 = lm(bwt ~ mrace + blength + momage, data = birthweight)

model_1 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

## Plot showing residuals against fitted values for Model 1 
birthweight %>% 
  add_residuals(model_1) %>%
  add_predictions(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() + 
  labs(
    x = "Predictive Values", 
    y = "Residual Values", 
    title = "Predictive Values vs. Residuals Values for Model 1"
  ) 
```

### Model 2 
```{r}
## Length at birth and gestational age as predictors (main effects only)
model_2 = lm(bwt ~ blength + gaweeks, data = birthweight) 

model_2 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

### Model 3
```{r}
## Head circumference, length, sex, and all interactions (including the three-way interaction) between these
model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight)

model_3 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Cross Validation
```{r}
## Cross validation 
cv_df = crossv_mc(birthweight, 100)

## Mapping 
cv_df = 
  cv_df %>% 
  mutate(model_1 = map(train, ~lm(bwt ~ mrace + blength + momage, data = .x)),
         model_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model_3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
         rmse_model_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))

## Cross Validation Plot 
cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() + 
  labs(
    x = "Model Number", 
    y = "RMSE", 
    title = "RMSE Values for Three Models for Birthweight Distribution"
  ) 
```

Plot Commentary: The prediction error between the 1st model I proposed and the 2nd model is fairly similar. However, the prediction error for the 3rd model is much smaller than the first two models. Therefore, the third model may be preferred. 