---
title: "Homework #6"
author: "Diana Ballesteros Gonzalez"
date: "11/27/2018"
output: github_document
---

```{r setup}
## Loading the packages
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = 1.0,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

### *Problem 1* 
```{r}
## Import data 
homicide_data = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = paste(city, state, sep = ", "))
```

Description of the raw data: The dataset gives you person information regarding all reported homicide in 50 major cities throughout the United States including first name, last name, race, age, and sex. The location information provides is city, state, longitude, and latitude information. Lastly, it includes information on the status of the case (i.e., open/no Arrest, Closed without arrest, or closed by arrest). Overall there are `r nrow(homicide_data)` reported cases and `r ncol(homicide_data)` variables in the dataset. 

Total number of homicides by city
```{r}
total_num_homicides_df = 
homicide_data %>% 
  group_by(city_state) %>% 
  summarize(total_num_homicides = n()) 
```

Number of unsolved homicides by city
```{r}
num_unsolved_homicides_df = 
homicide_data %>% 
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>% 
  group_by(city_state) %>% 
  summarize(num_unsolved_homicides = n()) 
```

```{r}
## Left join to combine both data frame  
all_df = 
  left_join(num_unsolved_homicides_df, total_num_homicides_df, by = "city_state")
```

Estimate the proportion of homicides that are unsolved for Baltimore, MD
```{r}
## Homicides for baltimore 
homicide_baltimore = 
  all_df %>% 
  filter(city_state == "Baltimore, MD")

## Creating a function for Baltimore, MD
prop_baltimore_function = function(num_unsolved_homicides,total_num_homicides) {
    prop.test(x = num_unsolved_homicides,
              n = total_num_homicides) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high)
}

# Estimate the proportion of homicides that are unsolved for Baltimore, MD
baltimore_prop = 
  map2(.x = homicide_baltimore$num_unsolved_homicides, 
       .y = homicide_baltimore$total_num_homicides,
       ~prop_baltimore_function(.x, .y)) %>% 
  bind_rows() %>% 
  bind_cols(homicide_baltimore) %>% 
  janitor::clean_names() %>% 
  select(city_state, num_unsolved_homicides, total_num_homicides, estimate, conf_low, conf_high)
```

```{r}
## Function for the proportion of unsolved cases 
prop_function = function(x,y) {
    prop.test(x = x,n = y) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high)
}

## Creating a data frame by mapping 
homicides_total = 
  map2(.x = all_df$num_unsolved_homicides, 
       .y = all_df$total_num_homicides,
       ~prop_function(.x, .y)) %>% 
  bind_rows() %>% 
  bind_cols(all_df) %>% 
  janitor::clean_names() %>% 
  select(city_state, num_unsolved_homicides, total_num_homicides, estimate, conf_low, conf_high)
```

Making a plot for the propotion of homicides

```{r}
## Create a plot with error bars 
homicides_total %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate, color = city_state)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) + 
  labs(
    title = "Proportion of unsolved homicide cases throughout 50 major US cities",
    x = "City Name",
    y = "Proportion of unsolved homicide cases"
  ) + 
  theme(legend.position = "none") + 
  theme(axis.text.x = element_text(angle = 90, size = 7))
```
