---
title: "Homework #6"
author: "Diana Ballesteros Gonzalez"
date: "11/27/2018"
output: github_document
---

```{r setup}
## Loading the packages
library(tidyverse)
library(purrr)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = 1.0,
  out.width = "90%"
)

set.seed(1)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

### **Problem 1**
```{r}
## Import data 
homicide_data = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = paste(city, state, sep = ", "), 
         resolved = as.numeric(disposition == "Closed by arrest"), 
         victim_age = as.numeric(victim_age),
         victim_race = ifelse(victim_race == "White", "White", "Non-White"), 
         victim_race = fct_relevel(victim_race, "White")) %>% 
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" & 
         city_state != "Kansas City, MO" & city_state != "Tulsa, AL") %>% 
  select(city_state, resolved, victim_age, victim_race, victim_sex)
```

```{r}
## Used the glm function to fit a logisitic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. 
fit_logistic = 
  homicide_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, 
      data = ., 
      family = binomial())

fit_logistic %>% 
  broom::tidy() %>% 
  filter(term == "victim_raceNon-White") %>% 
  mutate(OR = exp(estimate), 
         lower_limit = exp(estimate - 1.96*std.error), 
         upper_limit = exp(estimate + 1.96*std.error)) %>%
  select(OR, lower_limit, upper_limit) %>% 
  knitr::kable(digits = 3)
```

```{r}
nest_glm_res =
  homicide_data %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(resolved ~  victim_race + victim_age + victim_sex, 
                           data = .x, family = binomial)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
  mutate(OR = exp(estimate), 
         lower_limit = exp(estimate - 1.96 * std_error), 
         upper_limit = exp(estimate + 1.96 * std_error)) %>% 
  filter(term == "victim_raceNon-White") %>% 
  select(city_state, term, OR, lower_limit, upper_limit)

nest_glm_res %>% 
  knitr::kable(digits = 3)

nest_glm_res %>% 
  arrange(desc(OR)) %>% 
  mutate(city_state = fct_inorder(city_state)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymax = lower_limit, ymin = upper_limit)) +
  labs(
    x = "Location (City & State)", 
    y = "Estimated Odds Ratio of Resolved Cases for Non-Whites Compared to Whites", 
    title = "Estimated Odds Ratio of Resolved Homicide Cases for Non-Whites Compared to Whites throughout the United Sates"
  ) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```

Plot Commentary: 

### **Problem 2**
Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.


```{r}
## Import the data
birthweight = 
  read_csv(file = "./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~ "male",
      babysex == 2 ~ "female"), 
    babysex = fct_relevel(babysex, "male"), 
    
    frace = case_when(
      frace == 1 ~ "White", 
      frace == 2 ~ "Black", 
      frace == 3 ~ "Asian", 
      frace == 4 ~ "Puerto Rican", 
      frace == 8 ~ "Other", 
      frace == 9 ~ "Unknown"),
    frace = fct_relevel(frace, "White"), 
    
    malform = case_when(
      malform == 0 ~ "absent",
      malform == 1 ~ "present"), 
    malform = fct_relevel(malform, "absent"), 
    
    mrace = case_when(
      mrace == 1 ~ "White", 
      mrace == 2 ~ "Black", 
      mrace == 3 ~ "Asian", 
      mrace == 4 ~ "Puerto Rican", 
      mrace == 8 ~ "Other", 
      mrace == 9 ~ "Unknown"), 
    mrace = fct_relevel(mrace, "White")
    )
```

Description of the modeling process: 

* Mother's race, mother's age, and the the length of the baby are some factors that could potentially affect the baby's birthweight. 
```{r}
## Need to add labels and make it pretty 
model_1 = lm(bwt ~ mrace + blength + momage, data = birthweight)

model_1 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

modelr::add_residuals(birthweight, model_1)
modelr::add_predictions(birthweight, model_1)

birthweight %>% 
  add_residuals(model_1) %>%
  add_predictions(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() + 
  labs(
    x = "Predictive Values", 
    y = "Residual Values", 
    title = "Predictive Values vs. Residuals Values for Model 1"
  ) 
```


```{r}
## One using length at birth and gestational age as predictors (main effects only)
model_2 = lm(bwt ~ blength + gaweeks, data = birthweight) 

model_2 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

##One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight)

model_3 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```


```{r}
cv_df =
 crossv_mc(birthweight, 100)

cv_df = 
  cv_df %>% 
  mutate(model_1 = map(train, ~lm(bwt ~ mrace + blength + momage, data = .x)),
         model_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model_3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
         rmse_model_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() + 
  labs(
    x = "Model Number", 
    y = "RMSE", 
    title = "RMSE Values for Three Models for Birthweight Distribution"
  ) 
```


