---
title: "Homework #6"
author: "Diana Ballesteros Gonzalez"
date: "11/27/2018"
output: github_document
---

```{r setup}
## Loading the packages
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = 1.0,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

### *Problem 1* 
```{r}
## Import data 
homicide_data = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = paste(city, state, sep = ", "), 
         resolved = as.numeric(disposition == "Closed by arrest"), 
         victim_age = as.numeric(victim_age),
         victim_race = ifelse(victim_race != "White", "Non-White", "White"), 
         victim_race = fct_relevel(victim_race, "White", "non-White")) %>% 
  filter(city_state != "Dallas, TX" | city_state != "Phoenix, AZ" | 
         city_state != "Kansas City, MO" | city_state != "Tulsa, AL") 
```

```{r}
## Used the glm function to fit a logisitic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. 
fit_logistic = 
  homicide_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, 
      data = ., 
      family = binomial())

fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate), 
         lower_limit = exp(estimate - 1.96*std.error), 
         upper_limit = exp(estimate + 1.96*std.error)) %>%
  select(term, OR, lower_limit, upper_limit) %>% 
  filter(term == "victim_raceNon-White") %>% 
  knitr::kable(digits = 3)
```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}

```


